Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-18 Manuscript_draft/Text.Rmd
last results added to draft

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (*vegan* package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits. Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits for heterospecific pollen effect we used the function *bioenv* from R which finds the maximum rank of correlation among a subset of variables. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits. In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.

@@

Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances.

[Add Bioenv results](Jose)

The same analysis of Mantel test between HP pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area). When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a strong negative non significant correlation between style length and heterospecific pollen effect (Pearson's correlation=0.93, p=0.07) (see **Figure 7**).

>>>>

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (*vegan* package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the distance matrix of traits. Furthermore, the same analysis was conducted trait by trait in order to disentangled the specific effect of each trait. The correlation between heterospecific effect and traits was also looked at family level for Brassicaceae and Solanaceae species The family Convolvulaceae did not have enough species to test correlation with traits though Mantel test. Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits for heterospecific pollen effect we used the function *bioenv* from R which finds the maximum rank of correlation among a subset of variables. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits. In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.

@@

Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable/s with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances. The same analysis of Mantel test between heterospecific pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area). When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a positive and significant correlation between heterospecific pollen effect and pollen-ovule ratio
(r=0.74, one-tailed Mantel test p<0.05). Moreover, it seems to be a strong negative correlation between style length and heterospecific pollen effect although lack of significance (Pearson's correlation=0.93, p=0.07) (see **Figure 7**). For Brassicaceae species, the distance matrix of ovules and heterospecic pollen effect gave a positive and significant correlation (r=0.4, one-tailed Mantel test p<0.05).
